IRTF Spectro-Photometry of Two Rotating Brown Dwarfs: \\2MASS J08354256-0819237 and 2MASS J18212815+1414010

### 2016-11-19 ms.tex
I added a 2MASS J1821 label and an updated reference to the color magnitude diagram.
I turned off the rasterization of the image and added an acknowledgement to astropy.
I updated the time series plots to be in JD instead of saying orbital phase.

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{2mass_0835_t_series.pdf}
	\label{fig:tserPhase0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
	\label{fig:tserPhase1821}
	}
	\caption{Phase folded time series for both systems.}
	\label{fig:tserPfold}
\end{figure*}

@@

\section{Acknowledgements}
Thanks to Vivien Parmentier for useful discussions on cloud versus a spotted temperature model.
Funding for the E Schlawin is provided by NASA Goddard Spaceflight Center.
This research has made use of the Exoplanet Orbit Database and the Exoplanet Data Explorer at exoplanets.org.

@@

\section{Color-Magnitude Diagram}
\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{color_mag.pdf}
\caption{Color-Magnitude diagram from Dupuy and Liu.}\label{fig:CMD}
\end{centering}
\end{figure}

>>>>

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{2mass_0835_t_series.pdf}
	\label{fig:tserPhase0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
	\label{fig:tserPhase1821}
	}
	\caption{Time series for each system. Alternating colors are used to distinguished the light curves with offsets.}
	\label{fig:tserPfold}
\end{figure*}

@@

\section{Acknowledgements}
Thanks to Vivien Parmentier for useful discussions on cloud versus a spotted temperature model.
Funding for the E Schlawin is provided by NASA Goddard Spaceflight Center.
This research has made use of the Exoplanet Orbit Database and the Exoplanet Data Explorer at exoplanets.org.
This research made use of the \texttt{astropy} package \citep{astropy2013}.

@@

\section{Color-Magnitude Diagram}
\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{color_mag.pdf}
\caption{Color-Magnitude diagram from \citet{dupuy2012ltparallax}.}\label{fig:CMD}
\end{centering}
\end{figure}
